COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-04-15 main.tex
Dont build plots when compiling LaTeX, update abstract

\begin{abstract}
A perturbing planet can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs). Unfortunately,
the planetesimal-sized objects that make up the majority of these disks are extremely difficult to directly observe. Dust created from
collisions between planetesimals may be a much better way to constrain the structure of these disks. We use a direct N-body model
to measure planetesimal collision rates in a dynamically cold debris disk composed of 150 km bodies. Even though the eccentricities
are pumped at the nominal resonance locations, conservation of the Jacobi energy pushes planetesimals inward and enhances the
collision rate adjacent to the resonances. In addition, we find that the collision rate is severely throttled near the 3:1 MMR and that a
tightly wound spiral wave is launched from this location.
\end{abstract}

>>>>

\begin{abstract}
In circumstellar disks, collisional grinding of planetesimals produces second-generation dust, which can be observed through thermal 
emission. While it remains unclear when second-generation dust first becomes a major component of the total dust content, the presence of 
such dust and potentially the substructure within it can be used to explore a disk's physical conditions. A perturbing planet has been shown to 
produce nonaxisymmetric structures, as well as gaps in disks, regardless of the origin of the dust. However, small grains will have very 
different dynamics compared with planetesimals when in the presence of gas, and as such, the collisional evolution of planetesimals could 
create dusty disk structures that would not exist otherwise. In particular, mean motion resonances (MMRs) are extremely nonlinear and could 
drive disk morphologies. We use a direct N-body model to track collision rates in a planetesimal disk under the gravitational influence of an 
external Jupiter-sized planet. We show that a perturbing planet can produce significant variations in the collision rate of planetesimals near the 
MMRs and we explore how the mass and eccentricity of the perturbing planet alters this structure. Finally, we use the CASA image simulator to 
predict what the dust emission sturcture should look like with ALMA and the NG-VLA. Although the dust structure produced by MMRs cannot 
be used to directly measure the properties of the perturbing planet, we show that it can be used to place constraints on its mass and 
eccentricity.
\end{abstract}
